Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-13 paper-2024-sac-marl-neighbouring-strategies.tex
better fig 1

\subsection{Learning Schemes}
\begin{figure}
  \centering
  \includegraphics[width=0.49\linewidth]{figures/CTDE.pdf}
  %\vskip 1 mm
  \includegraphics[width=0.49\linewidth]{figures/DTDE.pdf}
  \caption{Graphical representation of CTDE (left) and DTDE (right) in MARL.}
  \label{fig:learning_paradigms}
\end{figure}
Multi-agent learning can be categorized based on the training scheme and the information accessibility for agents. 
Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE)---see \Cref{fig:learning_paradigms}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/behavior.pdf}
  \caption{Examples of cooperative and uncoordinated behavior. (Left) desired, agents effectively choose different paths to collect different items. (Right) undesired, agents cover the same path to collect the same item.}
  \label{fig:behavior}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/episode_reward_mean.pdf}
  \includegraphics[width=0.8\linewidth]{figures/episode_len_mean.pdf}
  \caption{Training performance of neighbor-based decentralized training strategies compared to centralized (CTDE) and fully decentralized (DTDE) approaches. 
  Two of the three neighbor-based methods achieve performance comparable to CTDE, 
  demonstrating the effectiveness of these methods in achieving scalability and coordination.
  }
  \label{fig:results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/scalability.pdf}
  \caption{Communication overhead (in MB) for different neighboring strategies as a function of the number of neighbors.
  }
  \label{fig:scalability}
\end{figure}

>>>>

\subsection{Learning Schemes}
\begin{figure}
  \centering
  \includegraphics[width=0.49\linewidth]{figures/CTDE.pdf}
  %\vskip 1 mm
  \includegraphics[width=0.49\linewidth]{figures/DTDE.pdf}
  \caption{Graphical representation of CTDE (left) and DTDE (right) in MARL.
  For simplicity, only two agents are represented. However, the model can easily be extended to the general case of N agents.}
  \label{fig:learning_paradigms}
\end{figure}
Multi-agent learning can be categorized based on the training scheme and the information accessibility for agents. 
Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE)---see \Cref{fig:learning_paradigms}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figures/behavior.pdf}
  \caption{Examples of cooperative and uncoordinated behavior. (Left) desired, agents effectively choose different paths to collect different items. (Right) undesired, agents cover the same path to collect the same item.}
  \label{fig:behavior}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.75\linewidth]{figures/episode_reward_mean.pdf}
  \includegraphics[width=0.75\linewidth]{figures/episode_len_mean.pdf}
  \caption{Training performance of neighbor-based decentralized training strategies compared to centralized (CTDE) and fully decentralized (DTDE) approaches. 
  Two of the three neighbor-based methods achieve performance comparable to CTDE, 
  demonstrating the effectiveness of these methods in achieving scalability and coordination.
  }
  \label{fig:results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figures/scalability.pdf}
  \caption{Communication overhead (in MB) for different neighboring strategies as a function of the number of neighbors.
  }
  \label{fig:scalability}
\end{figure}
